Security Metrics for the Android Ecosystem

### 2015-07-23 spsm04-thomas.tex
Keywords should be semicolon separated
Note the possibility of interpreters in threat model (R3)

\keywords{Android, updates, vulnerabilities, metrics, ecosystems}

@@

The \emph{dynamic code loading} attack vector is to make an existing app download and execute code at runtime.
The most direct method is to upload to a marketplace a seemingly innocent app that dynamically loads malicious code.
Neither static nor dynamic analysis of this app will uncover any malicious code, since it does not exist in the app.
The marketplace can detect explicit use of dynamic code loading, however dynamic code loading is not actually needed for this to work -- it just makes the task easier -- even on a platform such as iOS, which does not permit dynamic code loading, a Return-Oriented Programming (ROP) attack is relatively easy if the attacker creates an app with carefully crafted flaws~\cite{Wang2013a}.

>>>>

\keywords{Android; updates; vulnerabilities; metrics; ecosystems}

@@

The \emph{dynamic code loading} attack vector is to make an existing app download and execute code at runtime.
The most direct method is to upload to a marketplace a seemingly innocent app that dynamically loads malicious code, either as additional davik bytecode, as a native library or by embedding an interpreter and executing received instructions.
Neither static nor dynamic analysis of this app will uncover any malicious code, since it does not exist in the app.
The marketplace can try to detect explicit use of dynamic code loading, however there are ways to dynamically load code which are hard to detect even on a platform such as iOS, which does not permit dynamic code loading, a Return-Oriented Programming (ROP) attack is relatively easy if the attacker creates an app with carefully crafted flaws~\cite{Wang2013a}.
